---
title: "Examples of using twstats"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Basic example of using twstats

First, load the library:

```{r}
library(twstats)
```

First, find tables you are interested in. Generally you do this by specifying the columns:

```{r}
twstats_find_tables('year/country/value')
```

...you can also use wildcards if you don't care what sort of column it is:

```{r}
head(twstats_find_tables('*/value'))
```

Given a table name, you can get more detail:

```{r}
twstats_get_table('eurostat/tin00073/country:IS')[c('name', 'title', 'source')]
```

Finally, we can get the data itself by calling it's data function:

```{r, message=FALSE}
twstats_get_table('eurostat/tin00073/country:IS')$data()
```

The value column specifies any continuous numeric value.
It's actual name in the data tells you what the values represent.
In addition to the above, there are tables with multiple value columns, for comparison questions. For example:

```{r, message=FALSE}
twstats_get_table('eurostat/tin00073/country:DE/country:FR')$title
twstats_get_table('eurostat/tin00073/country:DE/country:FR')$data()
```
