---
title: "Using twstats in a tutorweb question"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Using twstats in a tutorweb question}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Using twstats in a tutorweb question

```{r, echo=FALSE}
library(twstats)

write_question <- function (qtext = qtext, qtable = d, choices = choices, choicescorrect = choices_correct) {
    paste0(qtext, "\n\n",
        paste0("[ ] ", choices, collapse = "\n"))
}
```
First, use ``twstats_find_tables`` to search for tables you can use:

The following will search for any tables with year & value columns, and have
roughly 10 rows in it.

```{r}
qn_tables <- twstats_find_tables('year/value', required_rowcount = 10)
head(qn_tables)
```

Take this list and hard-code into the question code. Set ``TW:PERMUTATIONS`` to the length of
this list. The resulting question code should look something like this:

```{r}
# TW:PERMUTATIONS=3

qn_tables <- c(
    'eurostat/tin00073/country:BE',
    'eurostat/tin00073/country:BG',
    'cbso/82610ENG/total')

question <- function(permutation, data_frames) {
    tbl <- twstats_get_table(qn_tables[[permutation]])
    d <- tbl$data()
    
    qtext = paste0(
        'The table below shows ', tbl$title, '.\n',
        'Find the difference of ', colnames(d)[[2]], ' between ', min(d$year), ' and ', max(d$year),"\n\n",
        paste(capture.output(print.data.frame(head(d))), collapse = "\n"))
    choices = c(
        d[d$year == max(d$year), 2] - d[d$year == min(d$year), 2],
        d[d$year == max(d$year), 2] - d[d$year == min(d$year), 2] - 10,
        (d[d$year == max(d$year), 2] - d[d$year == min(d$year), 2]) / 10)
    choicescorrect = c(TRUE, FALSE, FALSE)

    write_question(qtext = qtext, choices = choices, choicescorrect = choices_correct);
}
```

This means that the output for each perumutation will be stable, e.g:

```{r, message=FALSE}
cat(question(1))
```

```{r, message=FALSE}
cat(question(3))
```

## Updating a question with new data

To update a question, you need to preserve the order of existing tables in ``twstats_tables`` to ensure questions don't change.
Provide the existing list with ``previous_tables``, which will filter then from the result:

```{r}
twstats_find_tables('year/value', required_rowcount = 10,
    previous_tables = qn_tables)
```

Then add these tables to ``qn_tables`` in the question code, and increase ``TW:PERMUTATIONS`` accordingly.